Cybercrime and Online Video Games

### 2019-12-12 paper/paper.tex
Update paper.tex

\subsection{Key Players}
[A table would be a nice addition here]
[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
[WHICH CHEATS ARE MOST POPULAR]

>>>>

\subsection{Key Players}
In the context of our project, the key players in the Fortnite hacker forums are those who have the most threads and/or comments under their names. We defined a user as a key player if they posted more than one thread or more than fifty comments from our 104 threads and 7932 comments. We determined these metrics by manually analyzing the comments and threads and determining who were the minority of more active users. These active user threads will usually take the form of either crimeware or CaaS with the poster selling to whoever can pay with some supposedly “legal” methods scattered throughout. Some of the more popular services are account selling, radar hacks, aimbot hacks and cheaper V-Bucks. Below are two pie charts depicting the thread and comment counts with the labels identifying the greater contributors.

\subsubsection{Wyattz}
Wyattz can be considered the most active user on the Fortnite hacker forums being tied for the most threads at three and having the most comments at 162. Wyattz is also a veteran member of hackforums.net and appears to be a trusted source of “legal” software and methods. His Fortnite posts revolve around making money playing Fortnite using what he claims to be a legal method. Since we were unable to access his method we could not determine its legality but his customers have commented back with general satisfaction. The other factor that makes Wyattz interesting is his number of comments. These comments were not made on other threads but on his own. His comments are either responses to other user’s comments or simply declarations that he is online and ready to talk. Wyattz places a lot of effort into his work on hackerforum so even though his comments rarely range outside his own threads and his product is not explicitly illegal, he is still a major player worth looking at.

\subsubsection{Jombah}
Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and ___ comments. He still passes the threshold for being a key player but the reason he is being focused on is due to his product. Jombah sells Fortnite accounts which is one of the crimewares we are focusing on. Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify. Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers. Jombah’s relevance lies not with his stellar service but with the product he provides.

\subsubsection{Dylan}
The last key player we will feature is probably the most important figure in the overall Fortnite hackforum community, though that is not saying much. Dylan provides the cheats for users such as radar and silencers. His presentation and communication with clients is professionally done and there are very few complaints regarding his product. While this is important for Dylan’s hierarchy as a key player, what is most important about him is that he interacts with other Fortnite posters. While analyzing threads and comments, we noticed that very few posters comment beyond their threads. There is little to no communication among the Fortnite hackforum community. Dylan is the exception to the rule. He comments on other threads whether he is providing explanations of services, vouching for others or shooting down fraudulent products. Dylan is not the most active user in his community, but nobody is as far reaching making him the most important key player in this community.

%[A table would be a nice addition here]
%[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
%[WHICH CHEATS ARE MOST POPULAR]
